---
title: "Novelty Tagm Analysis"
author: "Oliver M. Crook"
date: "17 November 2018"
output: html_document
---
```{r,eval=FALSE}
devtools::install_github("lgatto/pRoloc", ref = "novelty" ,force = TRUE)
```


```{r,}
source("../scripts/plot2D.R")
myBlues <- colorRampPalette(RColorBrewer::brewer.pal(9,"Blues"))(100)
```

```{r,}
require(pRolocdata)
data(hirst2018)
newHirst <- hirst2018[, c(11:15, 26:30, 41:45)]
fData(newHirst)$markers[fData(newHirst)$markers == "Large Protein Complex"] <- "unknown"
load("hirstTagmNoveltyparams.rda")
setStockcol(paste0(getStockcol(), 90))
```

# check convergence
```{r,}
outliers <- mcmc_get_outliers(hirstTagmNoveltyparams[c(1,2,4,6)])
hirstdiag <- gelman.diag(outliers)
hirstTagmNoveltyparams_conv <- hirstTagmNoveltyparams[c(1,2,4,6)]
```


```{r,}
hirstTagmNoveltyRes <- tagmNoveltyProcess(object = newHirst, params = hirstTagmNoveltyparams_conv)
hirstTagmNoveltyparams_conv <- tagmMcmcProcess(hirstTagmNoveltyparams_conv)
newHirst <- tagmPredict(object = newHirst, params = hirstTagmNoveltyparams_conv)
save(hirstTagmNoveltyRes, file = "hirstTagmNoveltyRes.rda")
```


```{r,}
## attach information to MSnset
#fData(newHirst)$tagm.phenotype <- hirstTagmNoveltyRes$mpCombined$cl[rownames(fData(newHirst))]
#fData(newHirst)$tagm.discovery.prob <- hirstTagmNoveltyRes$tagm.discovery.prob[rownames(fData(newHirst))]

#fData(newHirst)$tagm.discovery.prob[is.na(fData(newHirst)$tagm.discovery.prob)] <- 0
newHirst <- tagmNoveltyPredict(object = newHirst, params = hirstTagmNoveltyRes)


ptsze <- exp(fData(newHirst)$tagm.discovery.prob) - 1
shade <-  exp(fData(newHirst)$tagm.mcmc.outlier) - 1
plot2D(newHirst, fcol = "tagm.phenotype", cex = ptsze)
addLegend(newHirst, fcol = "tagm.phenotype", ncol = 3, where = "topright", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- exp(fData(newHirst)$tagm.discovery.prob) - 1
ptsze[fData(newHirst)$tagm.mcmc.outlier < 0.0001] <- 0.01
plot2D(newHirst, fcol = "tagm.phenotype", cex = ptsze, main = "PCA of control HeLa data with pointer scaled to discovery probability", cex.main=2)
myleg <- levels(hirstTagmNoveltyRes@pooledNoveltyChain@mp@cl)
legend(7, 8, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(newHirst)$tagm.discovery.prob > 0.95) & fData(newHirst)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(newHirst)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(newHirst))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(hirstTagmNoveltyRes@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- as.character(levels(annot$organelle))

psmSub <- rownames(fData(newHirst))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(hirstTagmNoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the HeLa (Hirst et al.) data", color = myBlues, fontsize = 10, cellheight=0.5,cellwidth=0.7)
```

# Using plotPostSimMat in Proloc
```{r,}
toSubsethl <- (fData(newHirst)$tagm.discovery.prob > 0.95) & fData(newHirst)$tagm.mcmc.outlier < 0.95 
pRoloc:::plotPostSimMat(object = newHirst[toSubsethl],
                        params = hirstTagmNoveltyRes,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the HeLa (Hirst et al.) data",
                        fontsize = 10,
                        cellheight=0.5,
                        cellwidth=0.7)

```

# Go enrichment using cluster profiler
```{r,}
cc1Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 1" & 
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst))) # ribosome, cytosol

cc2Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 2" &
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst))) #extracellular, cytosol 

cc3Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 3" & 
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst))) # nothing

cc4Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 4"  
                                               & fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst))) # nothing

cc5Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 5" &
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst))) #

cc6Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 6" &
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst)))

cc7Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 7" &
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst)))

cc8Hirst <- enrichGO(gene = rownames(newHirst)[fData(newHirst)$tagm.phenotype == "Phenotype 8" &
                                                 fData(newHirst)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(newHirst)))
```
# Save results
```{r,}
ccHirstres <- list(cc1Hirst, cc2Hirst, cc3Hirst, cc4Hirst,
                   cc5Hirst, cc6Hirst, cc7Hirst, cc8Hirst)
save(ccHirstres, file = "ccHirstres.rda")
```


Beltran MOCK 24 analysis
```{r,}
load("beltranMOCK24TagmNoveltyparams.rda")
data("beltran2016MOCK24")
```

# check convergence
```{r,}
outliers <- mcmc_get_outliers(beltranMOCK24TagmNoveltyparams)
MOCK24diag <- gelman.diag(outliers)
```


```{r,}
beltranMOCK24TagmNoveltyRes <- tagmNoveltyProcess(object = beltran2016MOCK24, params = beltranMOCK24TagmNoveltyparams)
beltranMOCK24TagmNoveltyparams <- tagmMcmcProcess(beltranMOCK24TagmNoveltyparams)
beltran2016MOCK24 <- tagmPredict(object = beltran2016MOCK24, params = beltranMOCK24TagmNoveltyparams)
save(beltranMOCK24TagmNoveltyRes, file = "beltranMOCK24TagmNoveltyRes.rda")
```

```{r,}
## attach information to MSnset
#fData(beltran2016MOCK24)$tagm.phenotype <- beltranMOCK24TagmNoveltyRes$mpCombined$cl[rownames(fData(beltran2016MOCK24))]
#fData(beltran2016MOCK24)$tagm.discovery.prob <- beltranMOCK24TagmNoveltyRes$tagm.discovery.prob[rownames(fData(beltran2016MOCK24))]

#fData(beltran2016MOCK24)$tagm.discovery.prob[is.na(fData(beltran2016MOCK24)$tagm.discovery.prob)] <- 0

beltran2016MOCK24 <- tagmNoveltyPredict(object = beltran2016MOCK24, params = beltranMOCK24TagmNoveltyRes)

ptsze <- fData(beltran2016MOCK24)$tagm.discovery.prob
plot2D(beltran2016MOCK24, fcol = "tagm.phenotype", cex = ptsze)
addLegend(beltran2016MOCK24, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(beltran2016MOCK24)$tagm.discovery.prob
plot2D(beltran2016MOCK24, fcol = "tagm.phenotype", cex = ptsze, main = "PCA of MOCK fibroblast data with pointer scaled to discovery probability", cex.main = 2.5)
myleg <- levels(beltranMOCK24TagmNoveltyRes@pooledNoveltyChain@mp@cl)
legend(3, 2, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95) & fData(beltran2016MOCK24)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(beltran2016MOCK24)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(beltran2016MOCK24))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(beltranMOCK24TagmNoveltyRes@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(beltran2016MOCK24))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(beltranMOCK24TagmNoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the MOCK fibroblast data", col = myBlues)
```
Using pRoloc function for heatmap plotting
```{r,}
toSubsethl <- (fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95) & fData(beltran2016MOCK24)$tagm.mcmc.outlier < 0.95 
pRoloc:::plotPostSimMat(object = beltran2016MOCK24[toSubsethl],
                        params = beltranMOCK24TagmNoveltyRes,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the MOCK fibroblast data",
                        fontsize = 10)
```







```{r,}
cc1beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 1" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) #ribosome, large ribosomal subunit

cc2beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 2" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) # actin cytoskeleton 

cc3beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 3" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) # mitochondrial part/ peroxisome

cc4beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 4" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) # nothing
cc5beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 5" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) #ribsomal 

cc6beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 6" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) # large ribsomal subunit
cc9beltran <- enrichGO(gene = rownames(beltran2016MOCK24)[fData(beltran2016MOCK24)$tagm.phenotype == "Phenotype 9" & fData(beltran2016MOCK24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016MOCK24))) #nothing

```

Beltran HCMV 24 analysis
```{r,}
load("beltranHCMV24TagmNoveltyparams.rda")
data("beltran2016HCMV24")
```

```{r,}
beltranH24NoveltyRes <- tagmNoveltyProcess(object = beltran2016HCMV24, params = beltranHCMV24TagmNoveltyparams)
```

# check convergence
```{r,}
outliers <- mcmc_get_outliers(beltranHCMV24TagmNoveltyparams)
HCMV24diag <- gelman.diag(outliers)
```


```{r,}
beltranHCMV24TagmNoveltyparams <- tagmMcmcProcess(beltranHCMV24TagmNoveltyparams)
beltran2016HCMV24 <- tagmPredict(object = beltran2016HCMV24, params = beltranHCMV24TagmNoveltyparams)
#save(beltranHCMV24TagmNoveltyRes, file = "beltranHCMV24TagmNoveltyRes.rda")
```

```{r,}
## attach information to MSnset
beltran2016HCMV24 <- tagmNoveltyPredict(object = beltran2016HCMV24, params = beltranH24NoveltyRes)

ptsze <- fData(beltran2016HCMV24)$tagm.discovery.prob
plot2D(beltran2016HCMV24, fcol = "tagm.phenotype", cex = ptsze)
addLegend(beltran2016HCMV24, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(beltran2016HCMV24)$tagm.discovery.prob
ptsze[fData(beltran2016HCMV24)$tagm.mcmc.outlier < 0.0001] <- 0.01
plot2D(beltran2016HCMV24, fcol = "tagm.phenotype", cex = ptsze, main = "PCA of HCMV infected fibroblast data with pointer scaled to discovery probability", cex.main = 2)
myleg <- levels(beltranH24NoveltyRes@pooledNoveltyChain@mp@cl)
legend(3, 2, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(beltran2016HCMV24)$tagm.discovery.prob > 0.99) & fData(beltran2016HCMV24)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(beltran2016HCMV24)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(beltran2016HCMV24))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(beltranH24NoveltyRes@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(beltran2016HCMV24))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(beltranH24NoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the HCMV infected fibroblast data", col = myBlues, cellwidth = 2.5)
```
#Using pRoloc function
```{r,}
pRoloc:::plotPostSimMat(object = beltran2016HCMV24[toSubsethl],
                        params = beltranH24NoveltyRes,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the HCMV",
                        fontsize = 10)

```





```{r,}
cc1Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 1" & 
                                                             fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) #nucleoplasm, small ribosmal subunit/ribsome

cc2Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 2" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "cc",
               universe = rownames(fData(beltran2016HCMV24))) # 

cc3Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 3" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # mitochondrial part, mitchondriol enevelope

cc4Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 4" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # nuclear envelope

cc5Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 5" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # ribosome, large ribosomal subunit

cc6Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 6" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # nothing

cc7Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 7" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # nothing
cc8Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 8" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # nothing

cc9Hbeltran <- enrichGO(gene = rownames(beltran2016HCMV24)[fData(beltran2016HCMV24)$tagm.phenotype == "Phenotype 9" & fData(beltran2016HCMV24)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(beltran2016HCMV24))) # nothing
```
```{r,}
ccHbeltran <- list(cc1Hbeltran, cc2Hbeltran, cc3Hbeltran, cc4Hbeltran,
                   cc5Hbeltran, cc6Hbeltran, cc7Hbeltran, cc8Hbeltran,
                   cc9Hbeltran)
save(ccHbeltran, file = "ccHbeltran.rda")
```

## Mouse hyperLOPIT analysis

Begin by loading data files and removeing annotations.
```{r,}
load("hlmouseTagmNoveltyParams.rda")
data("hyperLOPIT2015")
hlmouse <- hyperLOPIT2015
fData(hlmouse)$markers[fData(hlmouse)$markers %in% c("40S Ribosome","60S Ribosome",
                                            "Nucleus - Chromatin", "Nucleus - Non-chromatin")] <- "unknown" 
```

# Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlmouseTagmNoveltyparams)
mouseDiag <- gelman.diag(outliers[c(2,4)])
```


```{r,}
hlmouseTagmNoveltyparams_conv <- hlmouseTagmNoveltyparams[c(2,4)]
hlmouseTagmNoveltyRes_conv <- tagmNoveltyProcess(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
hlmouseTagmNoveltyparams_conv <- tagmMcmcProcess(hlmouseTagmNoveltyparams_conv)
hlmouse <- tagmPredict(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
#save(hlmouseTagmNoveltyRes_conv, file = "hlmouseTagmNoveltyRes_conv.rda")
```

```{r,}
#load("C:/Users/OllyC/Desktop/NoveltyTagm/hlmouseTagmNoveltyRes.rda")

```

```{r,}
## attach information to MSnset
hlmouse <- tagmNoveltyPredict(object = hlmouse, params = hlmouseTagmNoveltyRes_conv)

ptsze <- fData(hlmouse)$tagm.discovery.prob
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hlmouse, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,16), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(hlmouse)$tagm.discovery.prob 
ptsze[fData(hlmouse)$tagm.mcmc.outlier > 0.001] <- 0.01
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze, main = "mESC",
       cex.main = 2)
myleg <- levels(hlmouseTagmNoveltyRes_conv@pooledNoveltyChain@mp@cl)
legend(6, 5, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1.5)
```

```{r,}
toSubsethl <- (fData(hlmouse)$tagm.discovery.prob > 0.99) & fData(hlmouse)$TAGM$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(hlmouse)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(hlmouse))[toSubsethl]
# Set up for heat map
psmSub <- rownames(fData(hlmouse))[toSubsethl]
ann_colors = list(
  organelle = c(getStockcol()[1:length(unique(fData(hlmouse[psmSub])$tagm.phenotype))])
)

names(ann_colors$organelle) <- as.character(unique(fData(hlmouse[psmSub])$tagm.phenotype))

# Create Heatmap of PSM to big too run subset to 
pheatmap(hlmouseTagmNoveltyRes_conv@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "mESC", col = myBlues, cellwidth = 0.75, fontsize = 14)
```
# using pROloc function
```{r,}
pRoloc:::plotPostSimMat(object = hlmouse[toSubsethl],
                        params = hlmouseTagmNoveltyRes_conv,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the mouse data",
                        fontsize = 10)
```


```{r,}
cc1hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 1" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # centrosome

cc2hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 2" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # chromosome and chromatin

cc3hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 3" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # nucleolus

cc4hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 4" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # ribosome

cc5hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 5" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # cilium doesnt make any sense

cc6hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 6" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #nothing

cc7hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 7" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # plasma membrane part

cc8hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 8" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # cytoskeletal

cc9hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 9" & fData(hlmouse)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # nothing

```


```{r,}
data("yeast2018")
load("hlyeastTagmNoveltyparams.rda")
```

```{r,}
hlyeastTagmNoveltyRes <- tagmNoveltyProcess(object = yeast2018, params = hlyeastTagmNoveltyparams)
save(hlyeastTagmNoveltyRes, file = "hlyeastTagmNoveltyRes.rda")
```

 Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlyeastTagmNoveltyparams)
yeastDiag <- gelman.diag(outliers[c(5,6)])
```

```{r,}
hlyeastTagmNoveltyRes <- tagmNoveltyProcess(object = yeast2018, params = hlyeastTagmNoveltyparams[c(5,6)])
#save(hlyeastTagmNoveltyRes, file = "hlyeastTagmNoveltyRes.rda")
```

```{r,}
hlyeastTagmNoveltyparams_conv <- tagmMcmcProcess(hlyeastTagmNoveltyparams[c(5,6)])
yeast2018 <- tagmPredict(object = yeast2018, params = hlyeastTagmNoveltyparams_conv)

```

```{r,}
## attach information to MSnset
yeast2018 <- tagmNoveltyPredict(object = yeast2018, params = hlyeastTagmNoveltyRes)

ptsze <- fData(yeast2018)$tagm.discovery.prob
plot2D(yeast2018, fcol = "tagm.phenotype", cex = ptsze)
addLegend(yeast2018, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```
```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,22), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(yeast2018)$tagm.discovery.prob 
ptsze[fData(yeast2018)$tagm.mcmc.outlier > 0.001] <- 0.01
plot2D(yeast2018, fcol = "tagm.phenotype", cex = ptsze, main = "bakers' yeast",
       cex.main = 2)
myleg <- levels(hlyeastTagmNoveltyRes@pooledNoveltyChain@mp@cl)
legend(9, 10, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1.5, pt.cex = 1)
```


```{r,}
toSubsethl <- (fData(yeast2018)$tagm.discovery.prob > 0.99) & fData(yeast2018)$tagm.mcmc.outlier < 0.95 
pRoloc:::plotPostSimMat(object = yeast2018[toSubsethl],
                        params = hlyeastTagmNoveltyRes,
                        main = "Heatmap of the posterior similarity matrix for the yeast data",
                        fontsize = 14)
```


```{r,}
toSubsethl <- (fData(yeast2018)$tagm.discovery.prob > 0.99) & fData(yeast2018)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(yeast2018)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(yeast2018))[toSubsethl]
# Set up for heat map
psmSub <- rownames(fData(yeast2018))[toSubsethl]
ann_colors = list(
  organelle = c(getStockcol()[1:length(unique(fData(yeast2018[psmSub])$tagm.phenotype))])
)

names(ann_colors$organelle) <- as.character(unique(fData(yeast2018[psmSub])$tagm.phenotype))

# Create Heatmap of PSM to big too run subset to 
pheatmap(hlyeastTagmNoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "bakers' yeast", col = myBlues, cellwidth = 0.5, fontsize = 14)
```

```{r,}
cc1hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 1"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # ER, cell periphery, vaculoas membrane, plasma membrane 

cc2hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 2"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # chromosome kintechore , chromsomal region

cc3hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 3"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # cytoskelton

cc4hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 4"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # mitchondrial intermembrane space

cc5hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 5"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # none

cc6hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 6"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) #none

cc7hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 7"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # intracellular immature spore, fungal-type cell wall

cc8hlyeast <- enrichGO(gene = rownames(yeast2018)[fData(yeast2018)$tagm.phenotype == "Phenotype 8"],
               OrgDb = "org.Sc.sgd.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(yeast2018))) # charperone complex 

```

## Make tile plot for goEnrichment results
```{r,}
yeastTile <- matrix(1, ncol = 4, nrow = 7)

colnames(yeastTile) <- c("Phenotype 1", "Phenotype 3", "Phenotype 4", "Phenotype 8")
rownames(yeastTile) <- c(ccYeastres[[1]]@result$Description[1], ccYeastres[[1]]@result$Description[4],
                         ccYeastres[[3]]@result$Description[6], ccYeastres[[4]]@result$Description[1], 
                         ccYeastres[[8]]@result$Description[c(1,5,10)])
yeastTile[ccYeastres[[1]]@result[,2][ccYeastres[[1]]@result[,2] %in%  rownames(yeastTile)], 1] <- ccYeastres[[1]]@result[,5][ccYeastres[[1]]@result[,2] %in%  rownames(yeastTile)]
yeastTile[ccYeastres[[3]]@result[,2][ccYeastres[[3]]@result[,2] %in%  rownames(yeastTile)], 2] <- ccYeastres[[3]]@result[,5][ccYeastres[[3]]@result[,2] %in%  rownames(yeastTile)]
yeastTile[ccYeastres[[4]]@result[,2][ccYeastres[[4]]@result[,2] %in%  rownames(yeastTile)], 3] <- ccYeastres[[4]]@result[,5][ccYeastres[[4]]@result[,2] %in%  rownames(yeastTile)]
yeastTile[ccYeastres[[8]]@result[,2][ccYeastres[[8]]@result[,2] %in%  rownames(yeastTile)], 4] <- ccYeastres[[8]]@result[,5][ccYeastres[[8]]@result[,2] %in%  rownames(yeastTile)]

df <- as.data.frame(yeastTile)
df_long <- melt(df)

gg <- ggplot(df_long) + geom_tile(aes(fill = value))

myCol <- brewer.pal(7,"YlGnBu")
pheatmap(-log10(yeastTile), cluster_rows = FALSE, cluster_cols = FALSE, treeheight_row = 0, treeheight_col = 0, main = "bakers' yeast", col = myCol, fontsize = 14, legend_breaks = c(0, 5, 10, 15, 20, max(-log10(yeastTile))), legend_labels = c("0", "5", "10", "15","20", "-log10(p.value)\n"),
legend = TRUE)
```


## Itzhak 2016
```{r,}
load("itzhak2016TagmNoveltyparams.rda")
data("itzhak2016stcSILAC")
fData(itzhak2016stcSILAC)$markers[fData(itzhak2016stcSILAC)$markers %in% c("Large Protein Complex")] <- "unknown"
itzhak2016 <- filterNA(itzhak2016stcSILAC)
normalise(itzhak2016, method = "vsn")
```

```{r,}
outliers <- mcmc_get_outliers(itzhak2016TagmNoveltyparams)
itzhak2016Diag <- gelman.diag(outliers[c(1,2,6)])
```

```{r,}
itzhak2016TagmNoveltyparams_conv <- itzhak2016TagmNoveltyparams[c(1,2,6)]
itzhak2016NoveltyRes <- tagmNoveltyProcess(object = itzhak2016, params = itzhak2016TagmNoveltyparams_conv)
itzhak2016TagmNoveltyparams_conv <- tagmMcmcProcess(itzhak2016TagmNoveltyparams_conv)
itzhak2016 <- tagmPredict(object  = itzhak2016, params = itzhak2016TagmNoveltyparams_conv)
save(itzhak2016NoveltyRes, file = "itzhak2016NovelyRes.rda")
```

```{r,}
itzhak2016 <- tagmNoveltyPredict(object = itzhak2016, params = itzhak2016NoveltyRes)

ptsze <- fData(itzhak2016)$tagm.discovery.prob
plot2D(itzhak2016, fcol = "tagm.phenotype", cex = ptsze)
addLegend(itzhak2016, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(itzhak2016)$tagm.discovery.prob 
plot2D(itzhak2016, fcol = "tagm.phenotype", cex = ptsze, main = "PCA of HeLa (itzhak 2016) data with pointer scaled to discovery probability",
       cex.main = 2)
myleg <- levels(fData(itzhak2016)$tagm.phenotype)
legend(13, 10, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(itzhak2016)$tagm.discovery.prob > 0.99) & fData(itzhak2016)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(itzhak2016)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(itzhak2016))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(itzhak2016NoveltyRes@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(itzhak2016))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(itzhak2016NoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the HeLa (Itzhak) data", color = myBlues )
```
## Using pRoloc function
```{r,}
pRoloc:::plotPostSimMat(object = itzhak2016[toSubsethl],
                        params = itzhak2016NoveltyRes,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the HeLa (Itzhak) data",
                        fontsize = 10)
                        
```


```{r,}
cc1itzhak2016 <- enrichGO(gene = rownames(itzhak2016)[fData(itzhak2016)$tagm.phenotype == "Phenotype 1" & fData(itzhak2016)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2016))) # mitochondrial membrane 

cc2itzhak2016 <- enrichGO(gene = rownames(itzhak2016)[fData(itzhak2016)$tagm.phenotype == "Phenotype 2" & fData(itzhak2016)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2016))) # cytosolic part / nucleolus

cc3itzhak2016 <- enrichGO(gene = rownames(itzhak2016)[fData(itzhak2016)$tagm.phenotype == "Phenotype 3" & fData(itzhak2016)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2016))) # chromsome/ chromatin

```

```{r,}
ccItzhak2016res <- list(cc1itzhak2016, cc2itzhak2016, cc3itzhak2016)
save(ccItzhak2016res, file = "ccItzhak2016res.rda")
```

# LOPIT DC U2OS
```{r,}
load("dcU2OSTagmNoveltyparams.rda")
data(lopitdcU2OS2018)
fData(lopitdcU2OS2018)$markers[fData(lopitdcU2OS2018)$markers %in% c("NUCLEUS/CHROMATIN","PROTEASOME",
                                                                           "RIBOSOME")] <- "unknown"

```

# assess convergence

```{r,}
dcOutlier <- mcmc_get_outliers(dcU2OSTagmNoveltyparams)
gelman.diag(dcOutlier[c(1,3,5)])
```

```{r,}
dcU2OSTagmNoveltyparams_conv <- dcU2OSTagmNoveltyparams[c(1,3,5)]
```

```{r,}
lopitdcNoveltyRes_conv <- tagmNoveltyProcess(object = lopitdcU2OS2018, params = dcU2OSTagmNoveltyparams_conv)
dcU2OSTagmNoveltyparams_conv <- tagmMcmcProcess(params = dcU2OSTagmNoveltyparams_conv)
save(dcU2OSTagmNoveltyparams_conv, file = "dcU2OSTagmNoveltyparams_conv.rda")
lopitdcU2OS2018 <- tagmPredict(object = lopitdcU2OS2018, params = dcU2OSTagmNoveltyparams_conv)
save(lopitdcNoveltyRes_conv, file = "lopitdcNoveltyRes_conv.rda")
```


```{r,}
## attach information to MSnset
lopitdcU2OS2018 <- tagmNoveltyPredict(object = lopitdcU2OS2018,
                                      params = lopitdcNoveltyRes_conv)


ptsze <- fData(lopitdcU2OS2018)$tagm.discovery.prob
plot2D(lopitdcU2OS2018, fcol = "tagm.phenotype", cex = ptsze)
addLegend(lopitdcU2OS2018, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```


```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,10), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(lopitdcU2OS2018)$tagm.discovery.prob
ptsze[fData(lopitdcU2OS2018)$tagm.mcmc.outlier > 0.0001] <- 0.01
plot2D(lopitdcU2OS2018 , fcol = "tagm.phenotype", cex = ptsze, main = "PCA of LOPIT-DC U2OS data with pointer scaled to discovery probability",
       cex.main = 2)
myleg <- levels(lopitdcNoveltyRes_conv@pooledNoveltyChain@mp@cl)
legend(10, 8, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.99) & fData(lopitdcU2OS2018)$tagm.mcmc.outlier < 0.00001 

# Create annotation 
annot <- data.frame(organelle = fData(lopitdcU2OS2018)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(lopitdcU2OS2018))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(lopitdcNoveltyRes_conv@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(lopitdcU2OS2018))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(lopitdcNoveltyRes_conv@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the U2OS LOPIT-DC data")
```

```{r,}
pRoloc:::plotPostSimMat(object = lopitdcU2OS2018[toSubsethl],
                        params = lopitdcNoveltyRes_conv,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the U2OS LOPIT-DC data",
                        fontsize = 10)
```

```{r,}
cc1DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 1" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # nothing

cc2DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 2" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # actin cytoskeleton

cc3DC<- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 3" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # nucleolus, ribsomal subunit

cc4DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 4" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # nucleolus

cc5DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 5" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # proteasome

cc6DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 6" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # extracellular matrix

cc7DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 7" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # myosin complex

cc8DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 8" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) #endosome / early endosome

cc9DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 9" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) #chromsome,

cc10DC <- enrichGO(gene = rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 10" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(lopitdcU2OS2018))) # mitchondrial membrane
```
```{r,}
goCCDCres <- list(cc1DC, cc2DC, cc3DC, cc4DC,
                  cc5DC, cc6DC, cc7DC, cc8DC,
                  cc9DC, cc10DC)
save(goCCDCres, file = "goCCDCres.rda")
```

```{r,}
hpa <- read.table("aal3321_Thul_SM_table_S11.csv", sep = ",", header = TRUE)
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 1"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]]
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 2"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]]
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 3"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]] #nucleus enriched
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 4"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]] #nucleus enriched
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 5"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]] #nucleaus enriched
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 6"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]]
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 7"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]] #nucleaus enriched
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 8"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]]
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 9"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]] #nucleaus enriched
annotations <- table(hpa[hpa[,3] %in% substr(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 10"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:20]]
```

## Itzhak 2017

```{r,}
data(itzhak2017)
fData(itzhak2017)$markers[fData(itzhak2017)$markers %in% c("Large Protein Complex")] <- "unknown"
itzhak2017 <- filterNA(itzhak2017[,c(1:18)])
load("itzhak2017TagmNoveltyparams.rda")
```


```{r,}
#itzhak2017NoveltyRes <- tagmNoveltyProcess(object = itzhak2017[,c(1:18)], params = itzhak2017TagmNoveltyparams_thinned)
#save(itzhak2017NoveltyRes, file = "itzhak2017NoveltyRes.rda")
```

## check convergece
```{r,}
outliers <- mcmc_get_outliers(itzhak2017TagmNoveltyparams)
itzhak2017diag <- gelman.diag(outliers[c(4,5)])
```

```{r,}
itzhak2017TagmNoveltyparams_conv <- itzhak2017TagmNoveltyparams[c(4,5)]
itzhak2017NoveltyRes <- tagmNoveltyProcess(object = itzhak2017, params = itzhak2017TagmNoveltyparams_conv)
itzhak2017TagmNoveltyparams_conv <- tagmMcmcProcess(itzhak2017TagmNoveltyparams_conv)
itzhak2017 <- tagmPredict(itzhak2017, params = itzhak2017TagmNoveltyparams_conv)
itzhak2017 <- tagmNoveltyPredict(itzhak2017, itzhak2017NoveltyRes)
save(itzhak2017NoveltyRes, file = "itzhak2017NoveltyRes.rda")
```



```{r,}
## attach information to MSnset
ptsze <- fData(itzhak2017)$tagm.discovery.prob
plot2D(itzhak2017, fcol = "tagm.phenotype", cex = ptsze)
addLegend(itzhak2017, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(itzhak2017)$tagm.discovery.prob
ptsze[fData(itzhak2017)$tagm.mcmc.outlier > 0.0001] <- 0.01
plot2D(itzhak2017 , fcol = "tagm.phenotype", cex = ptsze, main = "PCA of mouse neuron data with pointer scaled to discovery probability",
       cex.main = 2)
myleg <- levels(itzhak2017NoveltyRes@pooledNoveltyChain@mp@cl)
legend(7, 8, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(itzhak2017)$tagm.discovery.prob > 0.99) & fData(itzhak2017)$tagm.mcmc.outlier < 0.01 

# Create annotation 
annot <- data.frame(organelle = fData(itzhak2017)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(itzhak2017))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(itzhak2017NoveltyRes@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(itzhak2017))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(itzhak2017NoveltyRes@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the mouse neuron data")
```

## Using pRoloc functon
```{r,}
pRoloc:::plotPostSimMat(object = itzhak2017[toSubsethl],
                        params = itzhak2017NoveltyRes,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the U2OS LOPIT-DC data",
                        fontsize = 10)
```

```{r,}
cc1itzhak2017<- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 1" &
                                                       fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) # nucleolus

cc2itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 2" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) #chromatin, chromosome

cc3itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 3" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) 

cc4itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 4" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) 

cc5itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 5" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) 

cc6itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 6" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017))) 

cc7itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 7" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017)))#plasma membrane

cc8itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 8" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017)))
cc9itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 9" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017)))
cc10itzhak2017 <- enrichGO(gene = rownames(itzhak2017)[fData(itzhak2017)$tagm.phenotype == "Phenotype 10" &
                                                        fData(itzhak2017)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(itzhak2017)))
```
```{r,}
ccItzhak2017res <- list(cc1itzhak2017, cc2itzhak2017, cc3itzhak2017, cc4itzhak2017,
                     cc5itzhak2017, cc6itzhak2017, cc7itzhak2017, cc8itzhak2017,
                     cc9itzhak2017, cc10itzhak2017)
save(ccItzhak2017res, file = "ccItzhak2017res.rda")
```

## hyperLOPIT U2OS

```{r,}
data(hyperLOPITU2OS2018)
fData(hyperLOPITU2OS2018)$markers[fData(hyperLOPITU2OS2018)$markers %in% c("RIBOSOME 40S","RIBOSOME 60S",
                                                                   "CHROMATIN", "NUCLEUS")] <- "unknown"
load("hlU2OSTagmNoveltyparams.rda")
```

## assess convergence

```{r,}
u2osOutlier <- mcmc_get_outliers(hlU2OSTagmNoveltyparams)
gelman.diag(u2osOutlier[c(2,4)])
```

```{r,}
hlU2OSTagmNoveltyparams_conv <- hlU2OSTagmNoveltyparams[c(2,4)]
```

```{r,}
hlu2osNoveltyRes_conv <- tagmNoveltyProcess(object = hyperLOPITU2OS2018, params = hlU2OSTagmNoveltyparams_conv)
hlu2osNoveltyparams_conv <- tagmMcmcProcess(params = hlU2OSTagmNoveltyparams_conv)
hyperLOPITU2OS2018 <- tagmPredict(object = hyperLOPITU2OS2018, params = hlu2osNoveltyparams_conv)
hyperLOPITU2OS2018 <- tagmNoveltyPredict(object = hyperLOPITU2OS2018, hlu2osNoveltyRes_conv) 
save(hlu2osNoveltyRes_conv, file = "hlu2osNoveltyRes_conv.rda")
```

```{r,}
ptsze <- fData(hyperLOPITU2OS2018)$tagm.discovery.prob
plot2D(hyperLOPITU2OS2018, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hyperLOPITU2OS2018, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
## specify large margin on the right hand side using mar and use xpd = T to allow plotting
par(mar=c(5,4,4,14), xpd = T)

## add legend manually with legend, you will need to play with x and y coords in legend depending on your screen and rendering
ptsze <- fData(hyperLOPITU2OS2018)$tagm.discovery.prob
ptsze[fData(hyperLOPITU2OS2018)$tagm.mcmc.outlier > 0.00001] <- 0.01
plot2D(hyperLOPITU2OS2018 , fcol = "tagm.phenotype", cex = ptsze, main = "PCA of hyperLOPIT U2OS with pointer scaled to discovery probability",
       cex.main = 2)
myleg <- levels(hlu2osNoveltyRes_conv@pooledNoveltyChain@mp@cl)
legend(11, 10, legend = myleg, col = getStockcol(), bty = "n",
       pch = 19, cex = 1, pt.cex = 1)
```

```{r,}
toSubsethl <- (fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.99) & fData(hyperLOPITU2OS2018)$tagm.mcmc.outlier < 0.95 

# Create annotation 
annot <- data.frame(organelle = fData(hyperLOPITU2OS2018)$tagm.phenotype[toSubsethl])
rownames(annot) <- rownames(fData(hyperLOPITU2OS2018))[toSubsethl]
# Set up for heat map
ann_colors = list(
  organelle = c(getStockcol()[1:nlevels(hlu2osNoveltyRes_conv@pooledNoveltyChain@mp@cl)])
)
names(ann_colors$organelle) <- levels(annot$organelle)

psmSub <- rownames(fData(hyperLOPITU2OS2018))[toSubsethl]

# Create Heatmap of PSM to big too run subset to 
pheatmap(hlu2osNoveltyRes_conv@pooledNoveltyChain@psm[psmSub,psmSub], useRaster = TRUE, annotation_row = annot, show_rownames = F, show_colnames = F, annotation_colors = ann_colors, treeheight_row = 0, treeheight_col = 0, main = "Heatmap of the posterior similarity matrix for the U2OS data")
```
## Using pRoloc function
```{r,}
pRoloc:::plotPostSimMat(object = hyperLOPITU2OS2018[toSubsethl],
                        params = hlu2osNoveltyRes_conv,
                        subset. = TRUE,
                        main = "Heatmap of the posterior similarity matrix for the U2OS LOPIT-DC data",
                        fontsize = 10)
```

```{r,}
# which phenotypes are "nuclear" in HPA data
#substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 1"], 1, 6)
annotations <- table(hpa[hpa[,3] %in% substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 3"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:10]] # most nucleoplasm
annotations <- table(hpa[hpa[,3] %in% substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 4"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:10]] #mostly nucleoplasm with nucleoli second
annotations <- table(hpa[hpa[,3] %in% substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 5"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:10]] #nucleoplasm /cytosol
annotations <- table(hpa[hpa[,3] %in% substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 6"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:10]] #cytosol/nucleoplasm
annotations <- table(hpa[hpa[,3] %in% substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 8"], 1, 6), "U.2.OS.location"])
annotations[order(annotations, decreasing = T)[1:10]] #nuclear membrane

```


```{r,}
cc1hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 1" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) #ribosome

cc2hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 2" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # endosome

cc3hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 3" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # chrosome and chromatin

cc4hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 4" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # nucleolus (Nucleoli from HPA too)

cc5hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 5" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # nucleplasm

bp6hlu2os <- enrichGO(gene = substr(rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 6" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95], 1, 6),
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "MF",
               universe = rownames(fData(hyperLOPITU2OS2018))) # (HPA Cyosol/Nucleoplasm)

cc7hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 7" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # filament

cc8hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 8" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # nuclear membrane and nuclear envelope (HPA top annotation)

cc9hlu2os <- enrichGO(gene = rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 9" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95],
               OrgDb = "org.Hs.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hyperLOPITU2OS2018))) # nothing

```


```{r,}
## Shared dc and hyperlopit endosome
sum(rownames(lopitdcU2OS2018)[fData(lopitdcU2OS2018)$tagm.phenotype == "Phenotype 8" & fData(lopitdcU2OS2018)$tagm.discovery.prob > 0.95] %in% rownames(hyperLOPITU2OS2018)[fData(hyperLOPITU2OS2018)$tagm.phenotype == "Phenotype 2" & fData(hyperLOPITU2OS2018)$tagm.discovery.prob > 0.95])

```
