---
title: "SensitivityAnalysis"
author: "Oliver M. Crook"
date: "10/08/2020"
output: html_document
---

```{r,}
require(MSnbase)
require(pRoloc)
require(pRolocdata)
require(mcclust)
require(pheatmap)
require(coda)

source("machinelearning-framework-tagm-Novelty.R")
source("machinelearning-functions-tagm-Novelty.R")


```



Begin by loading data files and removeing annotations.
```{r,}
load("hlmouseTagmNoveltyParams_beta01.rda")
data("hyperLOPIT2015")
hlmouse <- hyperLOPIT2015
fData(hlmouse)$markers[fData(hlmouse)$markers %in% c("40S Ribosome","60S Ribosome",
                                            "Nucleus - Chromatin", "Nucleus - Non-chromatin")] <- "unknown" 
```


# Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlmouseTagmNoveltyparams_beta01)
mouseDiag <- gelman.diag(outliers[c(1,2)])
```


```{r,}
hlmouseTagmNoveltyparams_conv <- hlmouseTagmNoveltyparams_beta01[c(1)]
hlmouseTagmNoveltyRes_conv <- tagmNoveltyProcess(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
hlmouseTagmNoveltyparams_conv <- tagmMcmcProcess(hlmouseTagmNoveltyparams_conv)
hlmouse <- tagmPredict(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
```


```{r,}
## attach information to MSnset
fData(hlmouse)$tagm.phenotype <- hlmouseTagmNoveltyRes_conv@pooledRes@mp@cl[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob <- hlmouseTagmNoveltyRes_conv@tagm.newcluster.prob[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob[is.na(fData(hlmouse)$tagm.newcluster.prob)] <- 0

ptsze <- fData(hlmouse)$tagm.newcluster.prob
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hlmouse, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)
# Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlmouseTagmNoveltyparams_beta01)
mouseDiag <- gelman.diag(outliers[c(1,2)])
```


```{r,}
hlmouseTagmNoveltyparams_conv <- hlmouseTagmNoveltyparams_beta01[c(1)]
hlmouseTagmNoveltyRes_conv <- tagmNoveltyProcess(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
hlmouseTagmNoveltyparams_conv <- tagmMcmcProcess(hlmouseTagmNoveltyparams_conv)
hlmouse <- tagmPredict(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
```


```{r,}
## attach information to MSnset
fData(hlmouse)$tagm.phenotype <- hlmouseTagmNoveltyRes_conv@pooledRes@mp@cl[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob <- hlmouseTagmNoveltyRes_conv@tagm.newcluster.prob[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob[is.na(fData(hlmouse)$tagm.newcluster.prob)] <- 0

ptsze <- fData(hlmouse)$tagm.newcluster.prob
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hlmouse, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```


```{r,}
require(clusterProfiler)
require("org.Mm.eg.db")
cc1hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 1" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # chromosome

cc2hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 2" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # filament

cc3hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 3" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # cilium

cc4hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 4" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # centrosome

cc5hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 5" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # endosome

cc6hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 6" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #spindle

cc7hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 7" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc8hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 8" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc9hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 9" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

```

```{r,}
beta01res <- list(cc1hlmouse)
```


Begin by loading data files and removeing annotations.
```{r,}
load("hlmouseTagmNoveltyParams_beta02.rda")
data("hyperLOPIT2015")
hlmouse <- hyperLOPIT2015
fData(hlmouse)$markers[fData(hlmouse)$markers %in% c("40S Ribosome","60S Ribosome",
                                            "Nucleus - Chromatin", "Nucleus - Non-chromatin")] <- "unknown" 
```


# Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlmouseTagmNoveltyparams_beta02)
mouseDiag <- gelman.diag(outliers[c(1,2)])
```


```{r,}
hlmouseTagmNoveltyparams_conv <- hlmouseTagmNoveltyparams_beta02[c(2)]
hlmouseTagmNoveltyRes_conv <- tagmNoveltyProcess(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
hlmouseTagmNoveltyparams_conv <- tagmMcmcProcess(hlmouseTagmNoveltyparams_conv)
hlmouse <- tagmPredict(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
```


```{r,}
## attach information to MSnset
fData(hlmouse)$tagm.phenotype <- hlmouseTagmNoveltyRes_conv@pooledRes@mp@cl[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob <- hlmouseTagmNoveltyRes_conv@tagm.newcluster.prob[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob[is.na(fData(hlmouse)$tagm.newcluster.prob)] <- 0

ptsze <- fData(hlmouse)$tagm.newcluster.prob
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hlmouse, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
require(clusterProfiler)
require("org.Mm.eg.db")
cc1hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 1" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # chromosome

cc2hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 2" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #

cc3hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 3" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # ribosome

cc4hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 4" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #

cc5hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 5" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc6hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 6" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #

cc7hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 7" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc8hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 8" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc9hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 9" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

```

```{r,}
beta02res <- list(cc1hlmouse, cc3hlmouse)
```


Begin by loading data files and removeing annotations.
```{r,}
load("hlmouseTagmNoveltyParams_beta03.rda")
data("hyperLOPIT2015")
hlmouse <- hyperLOPIT2015
fData(hlmouse)$markers[fData(hlmouse)$markers %in% c("40S Ribosome","60S Ribosome",
                                            "Nucleus - Chromatin", "Nucleus - Non-chromatin")] <- "unknown" 
```

# Check convergence formally

```{r,}
outliers <- mcmc_get_outliers(hlmouseTagmNoveltyparams_beta03)
mouseDiag <- gelman.diag(outliers[c(4,5)])
```


```{r,}
hlmouseTagmNoveltyparams_conv <- hlmouseTagmNoveltyparams_beta03[c(4,5)]
hlmouseTagmNoveltyRes_conv <- tagmNoveltyProcess(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
hlmouseTagmNoveltyparams_conv <- tagmMcmcProcess(hlmouseTagmNoveltyparams_conv)
hlmouse <- tagmPredict(object = hlmouse, params = hlmouseTagmNoveltyparams_conv)
```


```{r,}
## attach information to MSnset
fData(hlmouse)$tagm.phenotype <- hlmouseTagmNoveltyRes_conv@pooledRes@mp@cl[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob <- hlmouseTagmNoveltyRes_conv@tagm.newcluster.prob[rownames(fData(hlmouse))]
fData(hlmouse)$tagm.newcluster.prob[is.na(fData(hlmouse)$tagm.newcluster.prob)] <- 0

ptsze <- fData(hlmouse)$tagm.newcluster.prob
plot2D(hlmouse, fcol = "tagm.phenotype", cex = ptsze)
addLegend(hlmouse, fcol = "tagm.phenotype", ncol = 2, where = "bottomleft", cex = 0.5)

```

```{r,}
require(clusterProfiler)
require("org.Mm.eg.db")
cc1hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 1" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # chromosome

cc2hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 2" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #

cc3hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 3" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # ribosome

cc4hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 4" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # nucleolus

cc5hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 5" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc6hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 6" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) #

cc7hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 7" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc8hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 8" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

cc9hlmouse <- enrichGO(gene = rownames(hlmouse)[fData(hlmouse)$tagm.phenotype == "Phenotype 9" & fData(hlmouse)$tagm.newcluster.prob > 0.95],
               OrgDb = "org.Mm.eg.db",
               keyType = "UNIPROT",
               ont = "CC",
               universe = rownames(fData(hlmouse))) # 

```

```{r,}
beta03res <- list(cc1hlmouse, cc3hlmouse, cc4hlmouse)

```

```{r,}
betares <- list(beta01res, beta02res, beta03res)
save(betares, file = "sensitivitybeta.rda")
```
